Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys

### 2024-12-03 paper/paper.qmd
completed appendix section and updated llm usage

### Data Cleaning
#### 2018 Individual Data
The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change. The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity. The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.

#### 2018 Summary Data
Cleaning Process for the 2018 Summary Data
To create the 2018 summary data, I built off the cleaned 2018 individual data. This approach was necessary because the 2021 data was only available in summarized form, not at the individual level. By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years. The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.

#### 2021 Summary Data 
The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action. I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse. For each category, I selected specific rows and converted raw data into percentages. The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages. Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.

@@

@@

>>>>

@@

TO DO: add / talk about difficulty and problems with survey data

@@

# Idealized methodology {#sec-idealized-meth}
## Survey objectives
The primary objective of this study is to explore the factors influencing the likelihood of individuals engaging in climate-friendly behaviors. Specifically, the study aims to identify the age groups that are least likely to participate in sustainable actions and investigate how education levels impact climate-friendly behaviors. The research also seeks to determine whether individuals who report being relatively informed about climate change causes are more likely to take action to mitigate it. The underlying assumption is that individuals with greater knowledge of climate change should be more inclined to adopt behaviors that reduce its impact. Additionally, the study will examine the barriers that prevent people from engaging in sustainable behaviors, with the goal of identifying strategies to make these actions more accessible, affordable, and easy to adopt. The overarching aim is to develop solutions to increase the likelihood of participation in climate-friendly behaviors by removing existing barriers and promoting sustainability across different demographic groups. Part of this involves determining the most effective platforms for disseminating information about climate change, specifically by identifying which communication methods resonate most with different age groups. The research will also explore the role of education systems in fostering climate awareness and encouraging sustainable actions from a young age. Ultimately, the findings aim to provide actionable solutions to promote wider participation in climate-friendly actions, contributing to the fight against climate change.

## Sampling approach
This study will target a diverse set of respondents across various age groups and demographic characteristics to gain a comprehensive understanding of climate-friendly behaviors and their drivers. The sample will be stratified to ensure representation across youth and adult demographics, enabling a comparison of climate knowledge and behaviors between generations. The study will start by sampling youth as young as age 12. This age group is chosen because children are old enough to understand the basics of climate change and the actions required to address it but still impressionable enough for their behaviors to be influenced by education and social interventions. By including participants starting at age 12, we aim to assess how effective climate change education in schools is and whether it is shaping climate-friendly behaviors in the younger generation.

In addition to youth, adults aged 18 and older will also be included to provide insight into longer-term behavioral trends, which may have been shaped by earlier education or a lack of education on the subject. The sampling will be stratified according to age, education level, income, and geographic location to capture a broad spectrum of experiences and perspectives on climate change and sustainability. Age groups will be divided into the following ranges: 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, and 65+, while education levels will range from middle school to postgraduate education. Income will be categorized as low (<$30,000), middle ($30,000–$99,999), and high (>$100,000), and participants will also be grouped based on urban, suburban, or rural geographic locations. This stratified sampling approach ensures a diverse representation of individuals, allowing for meaningful comparisons of climate knowledge and behaviors across different demographic groups.

## Respondant recruitment 
Participants will be recruited using a multi-channel approach to ensure broad representation across various age groups and geographic locations. For youth aged 12-17, recruitment will occur through schools, with cooperation from middle and high schools. District educational boards or individual teachers will be approached to distribute information about the survey, and parental consent will be obtained before participation. To recruit adults, online surveys will be distributed via social media, email lists, and relevant climate-focused online communities. Additionally, outreach will be conducted in community centers and public spaces to capture respondents from rural or underserved areas. Flyers, local advertisements, and community events will help ensure that the sample is representative of both urban and rural populations.

Incentives such as gift cards or a donation to a climate-focused charity will be offered to participants to encourage engagement and improve response rates, especially among younger participants who may be less inclined to participate without an incentive.

## Data Validation 
To ensure the validity and reliability of the data, several validation mechanisms will be employed. Responses will be reviewed for internal consistency, such as cross-checking whether respondents who claim high levels of climate change knowledge also report engaging in corresponding climate-friendly behaviors. Participants who provide inconsistent answers or fail to complete the survey will be excluded from the analysis. Additionally, respondents may be contacted for clarification if their answers are ambiguous or incomplete. This will ensure that the data accurately reflects the participant's true attitudes and behaviors.

# Weighting and Data adjustments
The data collected will be weighted to account for any imbalances in demographic representation within the sample. Statistical weighting will adjust for factors such as age, education level, income, and geographic location to ensure the sample accurately reflects the broader population. Weighting will correct for any over- or under-representation of specific demographic groups, allowing for more generalizable findings. Additionally, data will be adjusted for non-response bias, with greater weight given to underrepresented groups (e.g., certain age groups or income levels) to correct for gaps in participation.

## Budget
The budget for this study will cover several key areas essential for effective data collection and analysis. A portion of the budget will be allocated to the survey platform and software tools needed for data collection, such as online survey tools and platforms for both youth and adult respondents. Since incentives are critical to encouraging participation, especially from younger individuals, funds will also be used to provide gift cards or donations to climate-related charities as incentives. To reach a diverse demographic, outreach costs will also be factored in, including the production and distribution of flyers, local advertisements, and outreach at community centers or schools. Lastly, resources will be dedicated to data analysis, including the purchase of statistical software like SPSS or R for cleaning, coding, and analyzing the responses. The final portion of the budget will cover any miscellaneous costs such as obtaining parental consent forms, printing, and mailing physical surveys or communication materials.

## Survey design
The survey design will be structured to capture a range of demographic and behavioral data in order to address the research objectives. The survey will begin with demographic questions to capture essential background information, including age, education level, income, and geographic location. These variables will allow the analysis to identify how climate-friendly behaviors and knowledge vary across different groups. The primary focus will be on participants' climate change knowledge, specifically assessing their awareness of its causes, impacts, and potential solutions. Respondents will be asked to rate their perceived level of knowledge about climate change on a Likert scale, ranging from "not informed" to "very informed." They will also be prompted to identify key contributors to climate change, as well as actions individuals can take to mitigate its effects.

The next section of the survey will focus on climate-friendly behaviors, asking respondents to self-report on their engagement in specific actions such as reducing car use, purchasing electric vehicles, eating plant-based meals, recycling, and reducing household energy consumption. These behaviors will help determine the extent to which knowledge of climate change is translating into actions, as well as highlight potential gaps in engagement.

Following this, the survey will include a section on barriers to sustainable behaviors, exploring factors that may be preventing individuals from adopting more climate-friendly actions. Participants will be asked to identify reasons such as cost, convenience, lack of knowledge, or skepticism. This will allow the study to pinpoint the most significant obstacles to widespread adoption of sustainable practices and provide insight into potential solutions.

The final section will focus on how respondents prefer to receive information about climate change. Given the varying effectiveness of different communication channels for different age groups, the survey will include questions on the most effective platforms for disseminating climate change education, such as social media, school programs, TV ads, and email. By identifying these preferences, the study will be able to recommend the most suitable methods for spreading climate change awareness tailored to specific demographics.

Each section of the survey will include a combination of multiple-choice, Likert scale, and open-ended questions to capture both quantitative and qualitative data. The open-ended responses will allow for more nuanced insights into the reasons behind individuals' climate-related behaviors and barriers. The design will aim to balance simplicity with comprehensiveness to ensure that the survey is engaging and easy to complete while still gathering sufficient data to answer the research questions effectively.

## Tradeoffs and limitations
While this methodology is designed to be comprehensive, there are inherent trade-offs and limitations that must be considered. One key limitation is the reliance on self-reported data. Since participants will be answering questions based on their own recollections and perceptions, there is the potential for bias, such as over-reporting sustainable behaviors or under-reporting barriers to climate action. This could skew the findings, particularly if individuals respond in a socially desirable manner. Additionally, while efforts will be made to capture a representative sample, there is a possibility of sampling bias, especially in rural areas or among specific income groups who may have limited access to the survey. This could affect the generalizability of the results. Further, survey fatigue is a potential issue, particularly with younger participants who may lose focus or fail to complete longer surveys. To mitigate this, the survey will be kept concise, though the breadth of questions may still pose challenges. Finally, while statistical weighting and adjustments for non-response bias will be implemented, there is always some degree of uncertainty regarding the effectiveness of these methods in fully correcting for bias or imbalances in the sample. These limitations must be taken into account when interpreting the findings of this study.

## Idealized survey questions
Thank you for your participation in the 2024 Climate Change Survey. This survey aims to gather information about public attitudes and behaviors related to climate change, with a focus on understanding the factors that influence people's engagement in climate-friendly actions. Your participation is entirely voluntary, and you may withdraw at any time, for any reason, with no questions asked.

This survey collects data regarding your awareness of climate change, the actions you take to mitigate it, and the barriers that may prevent you from engaging in more sustainable behaviors. The data you provide will be kept confidential and will be used solely for research purposes. This survey is anonymous, and your responses will not be traceable back to you. The goal of this survey is to better understand the motivations, challenges, and opportunities related to climate action, with a view to improving strategies for promoting sustainability.

If you have any questions or concerns about this survey or its methodology, please feel free to contact Lexi Knight via email at lexi.knight\@mail.utoronto.ca. Any correspondence will remain confidential and will not be shared with any external parties.

**Screening and Consent:**

By checking this box, I consent to this survey collecting information about my awareness of climate change, the actions I take to address it, and the factors that influence my behavior for research

Correspondence will not be shared with any external parties.
-    I consent.

**Demographic Information: **
1. Whats your age? 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say
2. What is the highest level of education that you've completed? Some high school, High school diploma, Diploma / post secondary certificate (college, trade school). Bachelor's degree, Master's degree, Doctorate degree.

**Climate Change knowledge and Awareness:**
3. How would you rate your knowledge of the causes of climate change? Very informed, Somewhat informed, Neutral, Somewhat Uninformed, Very uninformed.
4. How confident are you in your understanding of how to mitigate climate change through individual actions? Very confident, Confident, Neutral, Somewhat confident, Not confident.

**Climate-Friendly Action: **
5. Which of the following climate-friendly actions do you regularly engage in? (Select all that apply). Reduce personal vehicle use (e.g., carpooling, using public transport, biking or walking shorter distances), Use / install energy-efficient appliances / devices (e.g., LED bulbs, smart thermostats), Eat a plant-based diet or reduce meat consumption, Recycle and compost, Purchase eco-friendly products (e.g., sustainable clothing, eco-conscious brands), Use renewable energy sources (e.g., solar panels, wind energy), None of the above, Other.
6. How often do you consider the environmental impact of your purchases? Always, Often, Sometimes, Rarely, Never

**Barriers to Sustainable Actions: **
7. What factors prevent you from engaging in more climate-friendly behaviors? (Select all that apply) Cost of sustainable products or services, Lack of time, Lack of knowledge about how to make sustainable choices, Convenience (e.g., environmentally harmful options are more accessible), Skepticism about the effectiveness of individual actions, No barriers (I already engage in sustainable behaviors), Other (please specify)
8. Do you feel that climate-friendly behaviors are affordable for people in your community? Yes, No, Not sure
9. Which of the following reasons best describe why you do not participate in more climate-friendly actions? (Select all that apply) I do not believe my individual actions will make a difference, I find it too difficult to make sustainable choices in my daily life, It is too expensive to adopt sustainable behaviors, I don’t know where to start or how to make a meaningful impact, Sustainable products or services are not easily available in my area, I do not feel that climate change directly affects me or my community, I am unsure about what actions are most effective in reducing climate change, I am not sure how to balance sustainable actions with my current lifestyle
10. If you have avoided taking climate-friendly actions, what do you believe would make it easier for you to participate in these behaviors? (Select up to three) Lower cost of sustainable products or services, More convenient access to sustainable options, Clearer information on how individual actions can make a difference, More education or awareness about climate change, Incentives (e.g., government subsidies, rewards) to take action, More social pressure or norms encouraging sustainable behavior, Other (please specify)
11. How much do you trust the information provided by the following groups on climate change? Government, Environmental NGOs, Local community organizations, Media (TV, online news), Social media influencers/bloggers, Scientists, I do not trust any of these sources
12. If the government provided more support for individuals to take climate-friendly actions, would this lead you to taking more environmentally friendly actions (e.g., incentives, education programs, reduced cost)? Yes, No, Not sure
13. How strongly do you agree with the following statement: "Taking climate-friendly actions is a personal responsibility." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
14. How strongly do you agree with the following statement: "The government or businesses should take more responsibility for addressing climate change than individuals." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
15. Do you think the reluctance to take action against climate change more due to a lack of knowledge about how to get involved, or is it primarily because sustainable actions are inconvenient for people? Lack of knowledge about how to take action, Inconvenience of sustainable actions, Both, Neither, Unsure

**Education and Information: **
16. How effective do you think current school programs are in educating students about climate change? Very ineffective, Somewhat ineffective, Neutral, Somewhat effective, Very effective
17. Which platforms do you find most effective for receiving information about climate change? Social media (e.g., Instgram, Facebook, Twitter, TikTok), School programs, TV/Youtube, News articles, Websites, Podcasts, Community events, Email newsletters.

**General Perception: **
18. Do you believe that individual actions can make a significant difference in combating climate change? Yes, No, Not sure

19. In your opinion, which of the following should be prioritized to encourage more sustainable behaviors? (Select up to two), Making sustainable actions more affordable, Providing more education and awareness about climate change, Improving the accessibility of sustainable options, Encouraging government policies and incentives for sustainable behaviors, Creating a societal norm where sustainable actions are expected and practiced

**Confirmation Message**

Thank you for your response. We greatly appreciate the time, effort, and honesty you dedicated to completing this survey. Your answers have been successfully recorded and will contribute significantly to our research!

# Additional data details
After data collection, the responses will be cleaned, coded, and analyzed using appropriate statistical methods. Analysis will focus on identifying correlations between demographic factors (age, education, income, geography) and engagement in climate-friendly behaviors. The data will also be examined for patterns in barriers to participation and preferences for information delivery. These findings will provide the basis for actionable recommendations to improve climate change education and encourage greater participation in sustainable behaviors.

## Simlation Process {sec-simulation-process}
For the purposes of this study, I simulated data to investigate various factors related to climate change behaviors, including demographics, education levels, awareness of climate change causes, and preferences for communication methods. The simulated dataset consists of 404 entries, each representing an individual. To create this dataset, I used the `tidyverse` and `arrow` packages in R and set a seed value `(set.seed(853))` to ensure the results were reproducible. I generated the following variables:

The age variable was sampled randomly from a range between 18 and 100 years old. For education, I created several categories, such as "high school or less," "some community college/trade school," and "postgraduate/professional school," with an option for "prefer not to answer." The informed variable was categorized into four levels, from "extremely informed" to "not at all informed," reflecting the extent to which individuals felt knowledgeable about climate change causes. To capture the likelihood of engaging in climate-friendly actions, I simulated the likelihood of taking action variable, with responses ranging from "already doing this or have done this" to "very unlikely." Finally, the communication method variable explored how individuals preferred to receive climate-related information, with options such as "Toronto.ca website," "social media platforms," and "advertising campaigns," among others.

I used random sampling to generate values for each of these variables, ensuring a broad range of responses. After generating the data, I summarized it to verify its structure and consistency. The dataset was then saved as a `.parquet` file for further analysis. This approach allowed me to simulate a diverse set of responses and explore potential relationships between demographic factors, climate awareness, and willingness to engage in climate-friendly behaviors, all while maintaining the flexibility of synthetic data.

## Data cleaning {#sec-data-cleaning}

### 2018 Individual Data
The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change. The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity. The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.

### 2018 Summary Data
Cleaning Process for the 2018 Summary Data
To create the 2018 summary data, I built off the cleaned 2018 individual data. This approach was necessary because the 2021 data was only available in summarized form, not at the individual level. By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years. The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.

### 2021 Summary Data 
The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action. I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse. For each category, I selected specific rows and converted raw data into percentages. The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages. Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.
